\documentclass[11pt, a4paper]{article}
\begin{document}
\title{Report Analyzer}
\maketitle


\begin{large}
The report analyzer is an extension to Houston that is going to help us study and detect the causes of malfunctions. Houston is now capable of running multiple missions in sequence and annexing the resultant reports into one. We can now generate an abundant amount of data to study the system's performance and behavior under a set of missions. The report analyzer is still under development but we can brainstorm in the ways it would work. 

We can start by looking into patterns that might have been generated in a test session. As an example; we command Houston to run x random missions, and after analyzing the output we see that all the missions after y are flagged as failed. This is interesting because we see that something goes wrong after execution of mission y. We do not know if the problem is directly linked to mission y or if the problem manifests due to a multiple set of factors. Our report analyzer would look into the exact action that was not completed and that caused the mission failures. After analyzing the data we see that all the missions failed because the takeoff command was not completed. Looking more into the metrics we see that the gap between the expected altitude (altitude for takeoff) and the altitude where the system stanch grew as the missions progressed. This can give us good insight of an internal problem that manifests overtime. We can find what parts of the system's source code are linked with the takeoff command then evaluate and correct if necessary. We can also use code coverage to narrow down the location of the possible cause of the malfunction and maybe even go further to automatic repair. 

The report analyzer can also help us understand the efficiency and performance of a system. Using the random generator we can change the expected energy use per meter and test the system to see if it successfully finishes the missions without violating battery intents. Then analyze the data and see which actions might have cause battery intents violations. 

This is an exciting part of the project because we are very close to start seeing the usefulness and novelty of Houston in action. 



\end{large}
\end{document}
